\cvsection{WORK EXPERIENCE}

\cvevent
    {2020 - 2022}
    {Fullstack Web Developer}
    {Pluralsight}
    {I worked as a Fullstack Web Developer at Pluralsight for almost three years. I contributed to the backend and frontend of many applications within Flow, a product aimed at collecting and visualizing development metrics. First, I was focused on data ingestion using Kafka and improving the performance of queries in their database. After that, I helped create new microservices inside the platform, allowing me to explore and update my frontend skills towards React.js and GraphQL.}
    {}
    {\cvlist {
        \item Django + React.js
        \item PostgreSQL + Kafka
        \item Kubernetes + Gitops + Docker
        \item JIRA as the issue tracking/SCRUM tool
    }}
    {}
\cvevent
    {2015 - 2020}
    {CTO and Co-Founder}
    {Intelivix}
    {I was the CTO (chief technology officer) of a law tech startup called Intelivix. My role over five years has included managing web, data, and scraping teams, setting technology goals for the company, budgeting and developing, and implementing research and innovation programs. We were invested in by FINEP and FACEPE, Brazilian agencies for science and startup support during that time. I designed the data pipeline for our main product: Legys Jurimetria. It constitutes a series of dashboards that help companies track legal cases that they are involved in. This way, legal teams could devise strategies to cope with similar issues instead of starting from scratch every time. This allowed them to expedite large numbers of cases, especially in small-claims court. This project initially involved scraping data from a variety of sources on the internet. Afterward, data was processed and enriched using ETL processes and integration with other cloud services. The finalized data was then displayed in a variety of Tableau dashboards focused on different characteristics, depending on what the legal team wanted to examine.}
    {}
    {\cvlist {
        \item Django + Backbone.js (Javascript) + HTML5 + Bootstrap Framework (CSS)
        \item Jupyter + Scrapy + Pandas + ScikitLearn + Luigi Framework
        \item PostgreSQL + ElasticSearch + MongoDB
        \item Ansible + Docker for deployments
        \item Amazon Web Services as Cloud Provider
        \item JIRA as the issue tracking/SCRUM tool
    }}
    {}
\cvevent
    {2013 - 2014}
    {Web Developer}
    {Claria Seguros}
    {Claria is an insurance broker agency. My role there was to develop an MVP around a product for selling car insurance. Implemented both frontend and backend of the web application and also worked on an automation code for scraping data from other insurance websites. This code allowed customers to quickly find the latest and best offers available in one place. AWS was used for hosting the application.}
    {}
    {\cvlist {
        \item Django + Scrapy + Celery (Python)
        \item Backbone.js (Javascript) + HTML5 + Bootstrap Framework (CSS)
        \item PostgreSQL
        \item Amazon Web Services as Cloud Provider
        \item JIRA as the issue tracking/SCRUM tool
    }}
    {}
\cvevent
    {2011 - 2013}
    {Developer and Co-Founder}
    {Widevis Tecnologia em Des. de Software LTDA}
    {Close to completing my master's degree, I started a company called Widevis. It was selected for a pre-incubation program by Porto Digital. We had access to classes on entrepreneurship and consulting, specializing in technology businesses. Our goal was to develop a social network to raise money for Brazilian soccer teams in exchange for the use of their stadiums, interactions with soccer players, and budget transparency.}
    {}
    {\cvlist {
        \item Django + Scrapy (Python)
        \item PostgreSQL
    }}
    {}
\cvevent
    {2008 - 2009}
    {Internship}
    {5IT Des. de Sistemas de Informação LTDA}
    {This was both a software development internship and a scientific initiation scholarship called BITEC from Euvaldo Lodi Institute (IEL). In this internship, I worked with a Cold Fusion web application connected to a MySQL Database.}
    {}
    {\cvlist {
        \item Adobe ColdFusion
        \item MySQL
    }}
    {}
